Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-17 paper_jasa.tex
figure 11

From the experimental data the visual $p$-values are estimated based on Definition \ref{dfn:pvalue}. Figure \ref{fig:pval_definition} displays resulting estimates for each lineup against the conventional $p$-value.  The pattern of visual $p$-values is interesting: for small $p$-values the visual estimates tend to be very small, while lineups with larger $p$-values result in very large visual estimate, 
% If there is a signal in the data plot, visual $p$-value has a tendency to take a smaller value (small enough to reject $H_0$) and if not it takes a larger value (large enough to not reject $H_0$) 
% 
 giving a clear indication to reject $H_0$ or not. This is why we do not see lot of visual $p$-values in between 0.05 and 0.8 especially for experiment 2. This guide the researcher to make decision confidently while conventional $p$-values take some marginal $p$-values for which researchers get confused whether to reject or 'not reject' $H_0$. For visual test this is not common.

@@

\begin{figure*}[hbtp]
   \centering
      \includegraphics[width=0.95\textwidth]{p_val_log_counts-a.pdf}
       \includegraphics[width=0.95\textwidth]{p_val_log_counts-b.pdf}
  %      \includegraphics[width=0.95\textwidth]{p_val_log_counts.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the sixty (60) individual lineups for experiment 1. %\blue{Red indicates the} plot with the lowest $p$-value, and 
       \blue{blue indicates the} actual data plot, when it is different from that with the lowest $p$-value. The columns of both top and bottom panel are ordered according to effect size, rows within panels show replicates for each parameter combination.
       %Rows correspond to $\beta$, smallest to largest values from top to bottom. Columns correspond to other experimental treatments, sample size $(n)$, error standard deviation $(\sigma)$, and replicate. Empty cells indicate no lineup for that combination of parameters. Highest counts tend to be the plot in the lineup having the lowest $p$-value.
       }
       \label{fig:P-val_log}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \includegraphics[width=0.95\textwidth]{p_val_log_counts2.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the seventy (70) individual lineups for experiment 2. \blue{Red indicates the} plot with the lowest $p$-value, and \blue{blue indicates} the actual data plot, when it is different from that with the lowest $p$-value. Rows correspond to $\beta$, smallest to largest values from top to bottom. Columns correspond to other experimental treatments, sample size $(n)$, error standard deviation $(\sigma)$, and replicate. Empty cells indicate no lineup for that combination of parameters. Highest counts tend to be the plot in the lineup having the lowest $p$-value, even more so than for experiment 1.}
       \label{fig:P-val_log2}
\end{figure*}

>>>>

From the experimental data the visual $p$-values are estimated based on Definition \ref{dfn:pvalue}. Figure \ref{fig:pval_definition} displays resulting estimates for each lineup against the conventional $p$-value.  The pattern of visual $p$-values is interesting: for small $p$-values the visual estimates tend to be very small, while lineups with larger $p$-values result in very large visual estimate, 
% If there is a signal in the data plot, visual $p$-value has a tendency to take a smaller value (small enough to reject $H_0$) and if not it takes a larger value (large enough to not reject $H_0$) 
% 
 giving a clear indication to reject $H_0$ or not. This is why we do not see lot of visual $p$-values  between 0.05 and 0.8 especially for experiment 2. This guides the researcher to make decision confidently while conventional $p$-values take some marginal $p$-values for which researchers get confused whether to reject or 'not reject' $H_0$. For visual test this is not common.

@@

\begin{figure*}[hbtp]
   \centering
      \includegraphics[width=0.95\textwidth]{p_val_log_counts-a.pdf}
       \includegraphics[width=0.95\textwidth]{p_val_log_counts-b.pdf}
  %      \includegraphics[width=0.95\textwidth]{p_val_log_counts.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the sixty (60) individual lineups for experiment 1. \blue{Red indicates the} plot with the lowest $p$-value, and 
       \blue{blue indicates the} actual data plot. %, when it is different from that with the lowest $p$-value. 
       The columns of both top and bottom panel are ordered according to effect size, rows within panels show replicates for each parameter combination.
       %Rows correspond to $\beta$, smallest to largest values from top to bottom. Columns correspond to other experimental treatments, sample size $(n)$, error standard deviation $(\sigma)$, and replicate. Empty cells indicate no lineup for that combination of parameters. Highest counts tend to be the plot in the lineup having the lowest $p$-value.
       }
       \label{fig:P-val_log}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
%       \includegraphics[width=0.95\textwidth]{p_val_log_counts2.pdf}
       \includegraphics[width=0.75\textwidth]{p_val_log_counts2-a.pdf}       
       \includegraphics[width=0.75\textwidth]{p_val_log_counts2-b.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the seventy (70) individual lineups for experiment 2. \blue{Red indicates the} plot with the lowest $p$-value. %, and \blue{blue indicates} the actual data plot, when it is different from that with the lowest $p$-value. 
       %Rows correspond to $\beta$, smallest to largest values from top to bottom. Columns correspond to other experimental treatments, sample size $(n)$, error standard deviation $(\sigma)$, and replicate. 
%       
Columns are ordered according to effect size, with rows showing replicates of the same parameter combination on top of each other.
       Empty cells indicate combination of parameters with fewer than five replicates. 
       Highest counts tend to be the plot in the lineup having the lowest $p$-value, even more so than for experiment 1.
       }
       \label{fig:P-val_log2}
\end{figure*}
